Co-citations in context

### 2019-06-04 cocit_r.tex
More revisions on 6/3/19

\emph{This paragraph needs work, but I wanted to create a placeholder for the introduction to this subsection} A central theme of this article is the misspecification of the model in Uzzi et al. in terms of its sampling from a broad dataset without consideration of observed citation practices where papers cite a high percentage of papers from within the discipline related to the paper, frequency of citation, and xxx. For example we found (\emph{cite the statistics from Sitaram's study and other references about citation practices.}) We demonstrate the effects of model misspecification and effectiveness of using disciplinary datasets to resolve those issues.

\emph{Text from George that may serve well with, or in place of the above as an introduction to this subsection.}  Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model. A  principal consideration, however, was to restrict model misspecification arising from disciplinarily irrelevant references. We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.

>>>>

\emph{This paragraph needs work, but I wanted to create a placeholder for the introduction to this subsection.  It uses some of the passages form the former chacko subsection.} We have conjectured that the approach of Uzzi et al. for generating journal-pair z-scores is misspecified in its sampling from a broad dataset and its disregard for the frequency with which journal pairs are cited. Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model, although our principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references. We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.  In this subsection we demonstrate the effects of model misspecification or Uzzi et al.'s approach and the effectiveness of using disciplinary datasets in resolving the concomitant issues with the former.
